Parameter estimation

### 2023-05-26 SFE-article/Sections/Thermo_imp.tex
26.05

	\begin{figure*}[H]
		\centering
		\includegraphics[trim = 1.5cm 11.5cm 2.5cm 10.0cm,clip,width=\textwidth]{Figures/MU.pdf}	
		\includegraphics[trim = 1.5cm 4.0cm 2.5cm 19.0cm,clip,width=\textwidth]{Figures/MU.pdf}	
		\caption{Viscosity obtained based on different correlations } 
		\label{fig: SFE_Properties_mu}
	\end{figure*}

@@

	\begin{figure*}[H]
		\centering
		\includegraphics[trim = 1.5cm 2.5cm 1.5cm 2.0cm,clip,width=0.95\textwidth]{Figures/KT.pdf}	
		\caption{Thermal conductivity obtained based on different correlations }
		\label{fig: SFE_Properties_kt}
	\end{figure*}

>>>>

	\begin{figure}[!h]
		\centering
		\includegraphics[trim = 1.5cm 12.0cm 14cm 10.0cm,clip,width=\columnwidth]{Figures/MU.pdf}	
		\includegraphics[trim = 1.5cm 4.0cm  14cm 19.0cm,clip,width=\columnwidth]{Figures/MU.pdf}	
		\caption{Viscosity obtained based on different correlations } 
		\label{fig: SFE_Properties_mu}
	\end{figure}

@@

	\begin{figure*}[H]
		\centering
		\includegraphics[trim = 1.5cm 14.25cm 14cm 2.0cm,clip,width=0.49\textwidth]{Figures/KT.pdf}	
		\includegraphics[trim = 1.5cm 2.8cm 14cm 13.75cm,clip,width=0.49\textwidth]{Figures/KT.pdf}	
		\caption{Thermal conductivity obtained based on different correlations }
		\label{fig: SFE_Properties_kt}
	\end{figure*}
